---
output: github_document
author: Konstantin Mingoulin
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# kmfars2

<!-- badges: start -->
<!-- badges: end -->

## The goal of *kmfars2* is to: 
* import year specific data on accidents in a specific format
* summarize the data
* create some basic maps

## Installation

You CANNOT install the released version of kmfars2 from [CRAN](https://CRAN.R-project.org) with:

``` {r eval=F}
install.packages("kmfars2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=F}
library(kmfars2)
df2<-fars_summarize_years(c(2014,2015,2016))
```

## External data

The package contains external data that can be used for testing. The data can be accessed by using the following code:
```{r eval=F}
system.file("extdata", "accident_2013.csv.bz2", package = "kmfars2")
system.file("extdata", "accident_2014.csv.bz2", package = "kmfars2")
system.file("extdata", "accident_2015.csv.bz2", package = "kmfars2")

```

