---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## This vignette document is the official description of the super advanced package that import data, summarizes and builds some fancy plots

## To use the package you will need:
* files that contain accident data in the format 'accident_%d.csv.bz2' in home directory of your project

***

## Detailed usage
* you can supply multiple years at once in
```{r eval=F}
fars_read_years(c(2015,2016,2017))
```
* if you are just interested in summary counts you can use
```{r eval=F}
fars_summarize_years(c(2015,2016,2017))
```
* the package allows for mapping of accidents over a county map in a single year:
```{r eval=F}
fars_map_state(state.num, year)
```

***
## Package also contains data 'accident-accident' that can be accessed as:
```{r eval=F}
data(package="kmfars2")
```

***
## External data

The package contains external data that can be used for testing. The data can be accessed by using the following code:
```{r eval=F}
system.file("extdata", "accident_2013.csv.bz2", package = "kmfars2")
system.file("extdata", "accident_2014.csv.bz2", package = "kmfars2")
system.file("extdata", "accident_2015.csv.bz2", package = "kmfars2")

```
